What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-24 android-stacks.tex
changing the focus. More inprovements in sec 2

@@

- opensource
- elements of archtecture.
- Inversion of control development model.
- Activity onStart onResume onStop...
- Acess and share resources...

>>>>

Android is an open source platform for mobile devices based on Linux kernel.
The plaftom is also comprised of a core Java library, a set of libraries third-party libraries e.g.  SQLite,
the Dalvik runtime environment, and the framework which provides higher-level services to the applications
running on the platform e.g., controlling activities or providing data access.

Android supports an event-driven development model. The main element responsible for 
receiving the GUI events is the Activity, it is the unity of user interaction and execution in
Android. Android also provides APIs for data storage, communication between Activities, 
and other services. Moreover, it also provide frameworks for concurrent developement (e.g. AsyncTask) 
which is higly encouraged in Android development due to plaftorm restrictions [shimidit and arie].
\footnote{Other elements compose an application such as the Intents, resources
but are out of the scope for this paper.}.

@@
